Poster figures

### 2025-02-27 analysis/poster_ncar/presentation_figures.Rmd
Fiigures

@@

```{r extent-delta, fig.height=11.99/cm, fig.width=19.39/cm}

@@

bias_plot <- function(hindcast_clim, which_version, which_lead) {
  hindcast_clim |> 
    _[version == which_version] |>
    _[month_diff == which_lead] |> 
    # dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
    # setnames(which_dataset, "obs") |>
    ggplot(aes(xgrid, ygrid)) +
    geom_contour_fill(aes(z = aice - obs, fill = after_stat(level)), 
                      breaks = AnchorBreaks(binwidth = 0.1, exclude = 0)) +
    # geom_contour2(aes(z = aice - obs), breaks = AnchorBreaks(binwidth = 0.1, exclude = 0),
    #               linewidth = 0.1) +
    scale_fill_divergent_discretised(paste0(which_version, " bias at leadtime ", which_lead, " months"),
                                     low = trans_pink,
                                     high = trans_blue) +
    geomcoord_antarctica +
    geom_antarctica_fill +
    facet_wrap(~ month, 
               labeller = labeller(month = setNames(months, month.abb)),
               nrow = 2) +
    wide_legend +
    tag_facets()
}

@@

```{r, fig.width=22.15/cm, fig.height=12.3/cm}
hindcast_clim |> 
  bias_plot("S2", 0)
```

```{r}
hindcast_clim |> 
  bias_plot("S1", 0)
```

```{r}
hindcast_clim |> 
  bias_plot("S2", 6)

@@

```{r}
hindcast_clim |> 
  bias_plot("S1", 6)
```

@@

  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  labs(y = "RMSE", 
       x = "Lag") +
  scale_color_models +
  scale_fill_models +
  facet_wrap(~ month, labeller = labeller(month = labels_month)) 
```

```{rrmse_persistence, fig.width=19.43/cm, fig.height=11.99/cm}
g %+% g$data[version != "climatology"]
```

```{rrmse_climatology, fig.width=19.43/cm, fig.height=11.99/cm}
g %+% g$data[version != "persistence"]
```

@@

```{r, fig.width=19.43/cm, fig.height=11.99/cm}
p <- g +
  coord_cartesian(xlim = c(0, 100))

@@

```{r fig-rmse_lon, fig.height=7, fig.width=10}
#| fig.cap: Meadian difference between RMSE of +S2 forecasts and persistence forecast at longitudinal bands.

@@

  scale_y_continuous(breaks = NULL, expand = c(0, 0)) +
  labs(fill = NULL, 
       y = "Lag") +
  wide_legend +
  facet_wrap(~ month, labeller = labeller(month = labels_month)) +
  theme(panel.background = element_blank(), 
        tagger.panel.tag.background = element_rect(colour = "white", fill = "white"), 
        plot.margin = theme_margin) +
  tag_facets(position = list(x = 0.08, y = 1, hjust = 0, vjust = 1)) +

@@

### Comparison with S1

```{r}
t_test <- function(x, y, ...) {

  test <- t.test(x, y, ...)

  list(low = test[["conf.int"]][1],
       high = test[["conf.int"]][2], 
       estimate = -diff(test$estimate), 
       p.value = test[["p.value"]]
  )
}

max_lag <- errors[version == "S1", max(lag)]

dif <- errors |> 
  na.omit() |> 
  _[obs_dataset == which_dataset] |>
  _[measure == "iiee"] |> 
  _[version != "persistence"] |> 
  _[lag <= max_lag] |> 
  dcast(time + time_forecast + member + lag ~ version, value.var = "value") |> 
  _[, t_test(na.omit(S1), na.omit(S2)), 
    by = .(lag, month(time_forecast))] |> 
  _[p.value > 0.01] |> 
  _[, .SD[which.min(lag)], by = month] |> 
  _[order(month), .(month, lag)]

labels_month_significant <- setNames(paste0(month.abb, " (", dif$lag, ")"),
                                     1:12)
```

```{r fig-iiee}
#| fig-cap: Median and 95% coverage of Integrated Ice Edge Error as a function of forecast lag for all forecast initialised on the first of each month for +S1 and +S2 hindcasts. For each month, the number in parenthesis indicates the minimum lag at which the the mean error of each model is not statistically significant at a 1% level using a two-sisded t-test.

errors |> 
  _[measure == "iiee"] |>
  _[obs_dataset == which_dataset] |>
  # _[, month := lubridate::month(time_forecast, label = TRUE)]  |> 
  _[, median_ci(value), 
    by = .(lag, version, measure, obs_dataset, month(time_forecast))] |> 
  ggplot(aes(lag, mid)) +

  geom_text(data = month_from_lag(15, 2), aes(y = Inf, label = month2), 
            size = 2.5,
            vjust = 1) +

  geom_text(data = month_from_lag(1, 2), aes(y = -Inf, label = lag), 
            size = 2.5,
            vjust = 0) +

  geom_ribbon(aes(ymin = low, 
                  ymax = high, 
                  color = version, 
                  fill = version), alpha = 0.1) +
  geom_line(aes(color = version), linewidth = 1) +

  # geom_errorbar(data = \(x) x[dif, on = .NATURAL][version == "S1"], 
  #              aes(x = lag, 
  #                  ymin = mid - (high - low), ymax = mid + (high - low))) +

  # geom_point(data = \(x) x[dif, on = .NATURAL][version == "S1"],
  # aes(lag, mid), size = 3, shape = 21) +

  scale_y_continuous(labels = labels_extent) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_color_models +
  scale_fill_models +
  labs(y = NULL, 
       x = "Lag") +
  #   scale_color_models +
  #   scale_fill_models +
  facet_wrap(~ month, labeller = labeller(month = labels_month_significant)) 
```

```{r}
last_plot() +
  coord_cartesian(xlim = c(0, 100))
```

>>>>

knitr::opts_chunk$set(cache = TRUE)

@@

```{r extent-delta, fig.height=11.99/cm, fig.width=23.59/cm}

@@

bias_plot <- function(hindcast_clim, which_version, which_lead) {
  hindcast_clim |> 
    _[version == which_version] |>
    _[month_diff == which_lead] |> 
    # dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
    # setnames(which_dataset, "obs") |>
    ggplot(aes(xgrid, ygrid)) +
    geom_contour_fill(aes(z = aice - obs, fill = after_stat(level)), 
                      breaks = AnchorBreaks(binwidth = 0.1, exclude = 0)) +
    # geom_contour2(aes(z = aice - obs), breaks = AnchorBreaks(binwidth = 0.1, exclude = 0),
    #               linewidth = 0.1) +
    scale_fill_divergent_discretised(paste0(which_version, " bias at ", which_lead, " months at lead time"),
                                     low = trans_pink,
                                     high = trans_blue) +
    geomcoord_antarctica +
    geom_antarctica_fill +
    facet_wrap(~ month, 
               labeller = labeller(month = setNames(months, month.abb)),
               nrow = 2) +
    wide_legend +
    tag_facets()
}

@@

```{r}
width_bias <- 22.15/cm
height_bias <- 12.3/cm
```

```{r bias_S2_0, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S2", 0)
```

```{r bias_S1_0, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S1", 0)
```

lead
```{r bias_S2_6, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S2", 6)

@@

```{r bias_S1_6, fig.width=width_bias, fig.height=height_bias}
hindcast_clim |> 
  bias_plot("S1", 6)
```

@@

  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  labs(y = "RMSE", 
       x = "Lead time") +
  scale_color_models +
  scale_fill_models +
  facet_wrap(~ month, labeller = labeller(month = labels_month)) 
```

```{r}
width_errors <- 19.43/cm
height_errors <- 11.99/cm
```

```{rrmse_persistence, fig.width=width_errors, fig.height=height_errors}
g %+% g$data[version != "climatology"]
```

```{rrmse_climatology, fig.width=width_errors, fig.height=height_errors}
g %+% g$data[version != "persistence"]
```

@@

```{r error_zoom, fig.width=width_errors, fig.height=height_errors}
p <- g +
  coord_cartesian(xlim = c(0, 100))

@@

```{r fig-rmse_lon, fig.height=11.99/cm, fig.width=23.1/cm}
#| fig.cap: Meadian difference between RMSE of +S2 forecasts and persistence forecast at longitudinal bands.

@@

  scale_y_continuous(breaks = NULL, expand = c(0, 0)) +
  labs(fill = NULL, 
       y = "Lead time") +
  wide_legend +
  facet_wrap(~ month, labeller = labeller(month = labels_month)) +
  theme(panel.background = element_blank(), 
        tagger.panel.tag.background = element_rect(colour = "white", fill = "white"), 
        plot.margin = theme_margin) +
  tag_facets(position = list(x = 0.08, y = 1, hjust = 0, vjust = 1)) +

@@
